\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Daniyal,
    middleinitial=Umer,
    lastname=Haral,
    email=daniyalharal100@gmail.com,
    phone=0300 4352760,
    linkedin=daniyal-umer-haral,
    github=daniyalumer,
    city=LHR,
    state=PK,
]

% ----- Education -----
\section{Education}

\experience{Bachelor of Science}{Artificial Intelligence}{Sept 2020}{Jun 2024}{
    Ghulam Ishaq Khan Institute (GIKI) \hfill GPA: 3.05 \newline
    %Super Duper University, Town, State \newline
}
\experience{TensorFlow Developer Professional}{DeepLearning.AI}{Sept 2023}{}{}
\vspace{-10pt}

% ----- Work Experience -----
\section{Work Experience}
\experience{Software Engineer - AI}{Naseeb Online Services (Pvt) Ltd - ROZEE.PK}{February 2025}{Present}{
    \achievement{
    Led the transition from \tech{SQL-based retrieval} to
    \tech{Elasticsearch-powered semantic search}, reducing candidate
    retrieval time by 50\% to match job descriptions with relevant
    candidates.
    }
    \achievement{
        Crafted a \tech{Retrieval-Augmented Generation (RAG)} pipeline for efficient CV search. Parsed a dataset of over 1 million CVs into \tech{JSON} using \tech{GPT-4o}, optimized semantic search mappings, and utilized \tech{OpenAI's text-embedding-3-large} model with \tech{LangChain}.
    }
    \achievement{
        Utilized \tech{hybrid search (BM25 + vector search)} using \tech{Elasticsearch} and \tech{OpenAI embeddings}, while fine-tuning \tech{query expansion} and \tech{synonym mapping} to enhance search relevance by 30\% and improve candidate-job matching efficiency.
    }
    \achievement{

        Deployed scalable \tech{Python} APIs with \tech{Flask-RESTx} for job-matching, optimizing query performance with vector-based retrieval. Integrated \tech{WhatsApp Web.js} for systemized candidate outreach, improving job conversion rates by 20\%.

    }
    % \achievement{

    %     Enhanced AI-driven ranking algorithms for job listings, leading to a 25\% improvement in candidate-job match relevance. Adopted \tech{ML} models and \tech{Elasticsearch} for personalized recommendations, improving candidate-job matching efficiency.

    % }
}

\experience{Associate Software Engineer - AI}{Datum Brain}{Aug 2024}{Febraury 2025}{
    \achievement{

        Developed scalable APIs using \tech{Python}, and \tech{Flask-RESTx}, to manage agricultural sensor data in \tech{MongoDB}, and \tech{Krakend} as API gateway for a Europe-based Climate Change Observer firm. Leveraged \tech{Docker}, and \tech{AWS} for DevOps, cutting deployment time by 50\% with automated \tech{Bash} scripts, contributing to ESG-focused climate monitoring solutions.

    }
    \achievement{

        Engineered robust \tech{RESTful APIs} in \tech{Go} for a Europe-based fintech
        platform, enabling \tech{SEPA} and \tech{SWIFT} transaction processing.
        Designed XSD-based data validation and transaction workflows,
        ensuring 100\% compliance with fintech regulations.

    }
    \achievement{

        Built a \tech{Selenium} scraper for \tech{PostgreSQL}, integrated \tech{GPT} with \tech{LangChain} for natural language querying, and created a \tech{Go-based chat API} with \tech{MongoDB} for GPT-driven \tech{SQL} and humanized results.

    }
    \achievement{

        Contributed to the \tech{Open-Source Dirtree} package that
        prints directory tree with respect to \tech{.gitignore}. Added directory argument support and implemented
        version control flags (-v/--version).

    }
}

\experience{Software Development Intern}{Techlogix}{June 2023}{Aug 2023}{
    \achievement{

        Executed the implementation of \tech{ASP.NET Core} banking application, emphasizing \tech{Clean Architecture} and \tech{MVC} patterns
        to develop highly maintainable codebases that reduced bug fixes by 40\%.

    }
    \achievement{

        Designed seamless \tech{RESTful API} designs and optimized database management, to handle over 1000 concurrent users.

    }
    \achievement{

        Deployed on \tech{Azure} and incorporated advanced \tech{Chatbot} features
        with \tech{HuggingFace} pretrained models into web application,
        resulting in a significant 30\% decrease in customer complaints,
        elevating user satisfaction.

    }
}

\experience{Data Science Intern}{Systems Ltd}{Jul 2022}{Sept 2022}{
    \achievement{

        Acquired \tech{Data Warehousing}, \tech{SSIS}, \tech{ETL} techniques, and \tech{SQL} skills. Assembled a pipeline to process 10,000 sales records.

    }
    \achievement{

        Harnessed \tech{Tableau} to craft comprehensive dashboards, graphs, and maps, facilitating data-driven decision-making and
        saving 50 hours monthly in report generation.

    }
    \achievement{

        Conducted \tech{Exploratory Data Analysis} and constructed an \tech{LSTM} predictive model achieving 90\% accuracy on time-series data.

    }
}

% ----- Technical Projects -----
\section{Technical Projects}

% \experience{RozeeGPT}{Naseeb Online Services (Pvt) Ltd - ROZEE.PK}{Feb 2025}{Present}{
%     \achievement{
%         Led the transition from \tech{SQL-based retrieval} to \tech{Elasticsearch-powered semantic search}, reducing candidate retrieval time by 50\%.
%     }
%     \achievement{
%         Applied \tech{hybrid search (BM25 + vector search)} using \tech{Elasticsearch} and \tech{OpenAI embeddings}, improving search relevance by 30\%.
%     }
%     \achievement{
%         Streamlined embedding storage and indexing methodologies, allowing for the rapid retrieval of over 1 million CVs in under 200 milliseconds, enhancing user experience during candidate searches and boosting recruiter productivity.
%     }
%     \achievement{
%         Fine-tuned \tech{query expansion} and \tech{synonym mapping} for more accurate candidate-job matching, enhancing recruiter efficiency.
%     }
% }

\experience{Lucid Transit}{Final Year Project}{Sept 2023}{May 2024}{
    \achievement{

        Fine-tuned \tech{YOLOv8} model on a dataset of 10,000 images, achieving 80\% mAP for identifying 7 Pakistani
        vehicle classes. Annotated 600 images for passenger counting,
        with \tech{YOLOv8} reaching a 65\% mAP. Integrated with \tech{HIKVISION CCTV
        system}.

    }
    \achievement{

        Developed a responsive web app using \tech{React} and \tech{Flask}, featuring an interactive dashboard for real-time monitoring of
        vehicle and passenger influx. \tech{RTSP} for seamless CCTV connection.
        Raised 200,000 PKR in funding from Pakistan Engineering Council.

    }
}

\experience{Dutch Doc Accessibility: AI-powered Q\&A for the Disabled}{Freelance Project}{June 2024}{July 2024}{
    \achievement{

        Spearheaded a Python-based initiative enhancing accessibility for disabled individuals, using \tech{OCR} text extraction, \tech{GPT
        API} for spell correction (80\% accuracy improvement), \tech{Transformers} for translation, summarization, question answering
        on Dutch legal documents, integrating \tech{Text-to-Speech} and \tech{Speech Recognition} models for information retrieval.

    }
}

\experience{Shopify Store Automation}{Freelance Project}{July
2024}{August 2024}{
    \achievement{
        Streamlined \tech{customer segmentation} using \tech{Python} and \tech{Shopify Admin API (GraphQL)}, enabling personalized marketing and engagement.
    }
    \achievement{
        Devised \tech{custom automation tools} for order processing, analytics,
        and inventory management, reducing manual effort by 40\%.
    }
}

\vspace{\baselineskip}
\vspace{\baselineskip}

\experience{DocumentChat}{Freelance Project}{June 2023}{July 2023}{
    \achievement{

        Engineered a \tech{RAG Chatbot} utilizing \tech{Python}, \tech{LangChain} and \tech{Llama Index} with \tech{OpenAI's GPT-3.5 turbo} model, facilitating research paper question answering and summarization. A time-saving tool for researchers, facilitating efficient analysis.

    }
    \achievement{

        Orchestrated an intuitive user interface using \tech{Streamlit}, integrating conversational history tracking.

    }
}

\experience{Exploratory Data Analysis}{Academic Projects}{2021}{2024}{
    \achievement{

        Datasets Analyzed: CIFAR-10, Pak-Wheels, Play Tennis, Breast Cancer, Titanic, Iris, Corn or Maize Leaf, Airbus Aircraft Detection, Movie Reviews, Twitter Tweets, UNSW NB15, Insurance, Balance Scale.

    }
}

\experience{Algorithms Implemented From Scratch}{Academic Projects}{2020}{2024}{
    \achievement{

        AI Algorithms: \tech{Linear Regression, Logistic Regression, Decision Trees, K-mean Clustering, SVM, ANN, CNN, RCNN, GAN, LSTM, Transformers}.
    }
}

% ----- Technical Skills -----
\section{Technical Skills}
\small
\begin{itemize} % Set the font size to normal
    \item
    \textnormal{/Languages/Frameworks/Tools/Technologies:\tech{\textbf{
    Python}}, \tech{\textbf{Go}},
    \tech{\textbf{C/C++}}, \tech{\textbf{Bash}}, \tech{\textbf{SQL}}, \tech{\textbf{Flask}},
    \tech{\textbf{Django}}, \tech{\textbf{Go-chi}},
    \tech{\textbf{fiber}}, \tech{\textbf{Krakend}}, \tech{\textbf{Casbin}},
    \tech{\textbf{LangChain}}, \tech{\textbf{Tensorflow}}, \tech{\textbf{Pytorch}},
    \tech{\textbf{Scikit-learn}},
    \tech{\textbf{HuggingFaceTransformers}}, \tech{\textbf{YOLO}},
    \tech{\textbf{Pandas}}, \tech{\textbf{NumPy}}, 
    \tech{\textbf{NLTK}}, \tech{\textbf{spaCy}}, \tech{\textbf{VectorDatabases}},
    \tech{\textbf{ElasticSearch}}, \tech{\textbf{PostgreSQL}},
    \tech{\textbf{MongoDB}}, \tech{\textbf{Redis}},
    \tech{\textbf{Linux}}, \tech{\textbf{Git}},
    \tech{\textbf{Github Actions}},
    \tech{\textbf{CI/CD}}, \tech{\textbf{AWS}},
    \tech{\textbf{Terraform}}, \tech{\textbf{Docker}},
    \tech{\textbf{Postman}}, \tech{\textbf{EDA}}, 
    \tech{\textbf{ETL}}, \tech{\textbf{ML}}, \tech{\textbf{DL}},
    \tech{\textbf{NLP}}, \tech{\textbf{CV}}}
\end{itemize}

\end{document}